Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
S: Empower teams

@@

>>>>

* What are the agile principles? What is being talked about when ``agile
  principles'' is referred to?

@@

\subsubsection{Enable autonomy}

% Empowering teams

The agile principle of giving teams the power to decide over themselves was seen
as an important factor in advancing the transformation.
In some cases management initially attempted to prescribe how the new practices
should be implemented [P5, P18, P41]. However, it was learned that only when
full control was given to teams the agile methods could be properly established
[P5, P16, P41].
Allowing self-organization will create commitment to the change and motivation
to continued use [P16, P18]. It will allow teams to take ownership of the
development model and voluntarily improve it even further [P41].

The acceptance of agile methods was easy when teams gained authority to decide
on development speed and quality [P45]. Favoring empowerment over prescribing
the new practices was also reported to improve performance [P27]. Giving teams
authority to decide over work items increased productivity and morale [P30,
P34].

Roche and Vasquez-McCall [P41] describe how prescribing the agile methods to use
lead only so-far in the transformation. The effectiveness of teaching and
communicating the transformation started to decline. To enable the
transformation to still proceed, the an organization-wide challenge was created
where teams would independently develop and showcase the best agile practices.
As a result the ownership of the methods was transfered to teams, and the new
model gained a secure foothold. [P41]
